2024 US Presidential Election Model

### 2024-10-20 paper/paper.qmd
committing latex changes for model section

## Model set-up
Define \( y_i \) as the binary outcome variable indicating whether Donald Trump is predicted to win state \( i \) (1 if Trump wins, 0 if Harris wins). The predictor variables are \( \beta_i \), the average percentage of polling support for Donald Trump in state \( i \), and \( \gamma_i \), the average percentage of polling support for Kamala Harris in state \( i \).

>>>>

## Model set-up
Define $y_i$ as the binary outcome variable indicating whether Donald Trump is predicted to win state $i$ (1 if Trump wins, 0 if Harris wins). The predictor variables are $ \beta_i $, the average percentage of polling support for Donald Trump in state $i$, and $ \gamma_i $, the average percentage of polling support for Kamala Harris in state $i$.
